---
title: "Moving window analysis of cell number density of lymph node images"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This repository contains source codes of moving-window cell density analysis presented in the paper <title> and examples of the analysis. 


## Prerequisit

The actual analyses are done in R. However, core functions of obtaining 3D geometric intersections and volumes were imported from the geometric libraries, libigl and CGAL written in c++ through the Rcpp package. Thus, users are required to install libigl (https://libigl.github.io) and CGAL (https://doc.cgal.org/latest/Manual/usage.html). Additionally, Eigen (https://eigen.tuxfamily.org/dox/GettingStarted.html), Boost (https://www.boost.org/), GMP (https://gmplib.org/) and MPFR (https://www.mpfr.org/) are required to run libigl and CGAL libraries.


## How to use
 
Download and copy the files functions.R, mesh_boolean_R.cpp, and mesh_volume_R.cpp to a folder where you perform your analysis. 

### Load R packages
```{r cars}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
